Optimal Particle Paths Around Points in $\R^2$ with Constrained Acceleration

### 2013-10-08 path_theorems.tex
Changing wording and adding filler.

The simplest problem to tackle first, is the optimal trajectory from a starting position, $\bvec{X_0}$ to a final position, $\bvec{X_f}$. Working in a polar coordinate system centered on $X_f$, it is clear, that our goal is achieved when $r = 0$. Furthermore, $\theta(t)$ must be $0$ before reaching $X_f$, otherwise, it will grow exponentially fast as $r(t) \to 0$, which can be seen in equation (\ref{eq:r-deriv}).

\begin{lemma}
If $a_t=0$ and $a_c \le a_{c,max}$, then the minimum radius of curvature of a particle's trajectory is given by
\begin{equation}
R_{min} = \frac{v^2}{a_{c,max}}
\end{equation}
\end{lemma}

\begin{proof}
This comes directly from the definition of radius of curvature

@@

\[
a_c \le a_{c,max} \to \frac{1}{a_c} \ge \frac{1}{a_{c,max}}
\]
\end{proof}

>>>>

The simplest problem to tackle first, is the optimal trajectory from a starting position, $\bvec{X_0}$ to a final position, $\bvec{X_f}$. Working in a polar coordinate system centered on $\bvec{X_f}$, it is clear, that our goal is achieved when $r = 0$. Furthermore, $\theta(t)$ must be $0$ before reaching $\bvec{X_f}$, otherwise, it will grow exponentially fast as $r(t) \to 0$, which can be seen in equation (\ref{eq:r-deriv}).

\begin{lemma}
  If $a_t=0$ and $a_c \le \bar{a}_{c}$, then the minimum radius of curvature of a particle's trajectory is given by
\begin{equation}
  R_{min} = \frac{v^2}{\bar{a}_{c}}
\end{equation}
\end{lemma}

\begin{proof}
This comes directly from the definition of radius of curvature for a particle without any tangential acceleration:

@@

\[
  a_c \le \bar{a}_{c} \to \frac{1}{\bar{a}_c} \ge \frac{1}{\bar{a}_{c}}
\]
\end{proof}

We cann also investigate how the particle moves along a fastest path. In particle, we can make some statements about the change in $\theta$, the angle between the particle's velocity vector and the straight line between the particle and it's destination.
